---
title: "VAT08 Stage 1 and 2 nAb Data Batch Adjustment"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: false
    toc_depth: 3
    number_sections: true
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)

library(survey)
library(kyotil)

country.codes=c("Colombia", "Ghana", "Honduras", "India", "Japan", "Kenya", "Nepal", "United States", "Mexico", "Uganda", "Ukraine")
region.1 = c( # stage 1
  "United States" = 1, "Japan" = 1, 
  "Colombia" = 2, "Honduras" = 2, 
  "Ghana" = 3, "Kenya" = 3, 
  "Nepal" = 4, "India" = 4)
region.2 = c( # stage 2
  "Colombia" = 1, "Mexico" = 1, 
  "Ghana" = 2, "Kenya" = 2, "Uganda" = 2,
  "Nepal" = 3, "India" = 3)


dat_mapped=read.csv('/trials/covpn/p3005/analysis/mapping_immune_correlates/combined/adata/COVID_Sanofi_stage1and2_mapped_20240620_hotdeck.csv')
# dat_proc = read.csv('/trials/covpn/p3005/analysis/correlates/Part_A_Blinded_Phase_Data/adata/vat08_combined_data_processed_20240620.csv')

assay_metadata=read.csv('~/correlates_reporting2/assay_metadata/vat08_combined_assay_metadata.csv')
assays=assay_metadata$assay

bassays=assays[startsWith(assays,"bindSpike")][1:8]
print(bassays)

nassays=assays[startsWith(assays,"pseudoneutid50")][1:5]
print(nassays)

col1=1
col2=2
```


```{r impute_BA45, include=FALSE}

# impute BA45

library(mice)

kp=with(dat_mapped, !is.na(Bpseudoneutid50_BA.1) | !is.na(Bpseudoneutid50_BA.2) | !is.na(Bpseudoneutid50_BA.4.5)
                                | !is.na(Day22pseudoneutid50_BA.1) | !is.na(Day22pseudoneutid50_BA.2) | !is.na(Day22pseudoneutid50_BA.4.5)
                                | !is.na(Day43pseudoneutid50_BA.1) | !is.na(Day43pseudoneutid50_BA.2) | !is.na(Day43pseudoneutid50_BA.4.5))
        
imp.markers = c("Bpseudoneutid50_BA.1", "Bpseudoneutid50_BA.2", "Bpseudoneutid50_BA.4.5",
                                "Day22pseudoneutid50_BA.1", "Day22pseudoneutid50_BA.2", "Day22pseudoneutid50_BA.4.5",
                                "Day43pseudoneutid50_BA.1", "Day43pseudoneutid50_BA.2", "Day43pseudoneutid50_BA.4.5")

imp=dat_mapped[kp, imp.markers]
# mypairs(imp) # high cor at the same time point

imp <- mice(imp, m = 1, printFlag = FALSE, seed=1, diagnostics = FALSE , remove_collinear = FALSE)         

dat_mapped[kp, imp.markers] <- mice::complete(imp, action = 1)

```

```{r plotting_func, include=FALSE}

# putpairs of markers side by side
make.boxplots=function(st, .trt, day){
  tmp=subset(dat_mapped, Trialstage==st & Bserostatus==1 & Trt==.trt)
  # col=tmp$EventIndFirstInfectionD1+1
  
  ncol=10
  par(mfrow=c(1,ncol), oma=c(0,0,3,0), mar=c(5.1, 0.1, 2.1, 0.1), mgp = c(2, 1, 0))
  
  myboxplot(as.formula(day%.%"pseudoneutid50~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
  myboxplot(as.formula(day%.%"bindSpike~nAbBatch"),      tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2) 
  title(main="Ancestral", outer=T, line=-.5, adj=1/ncol)
  
  myboxplot(as.formula(day%.%"pseudoneutid50_B.1.351~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
  myboxplot(as.formula(day%.%"bindSpike_beta~nAbBatch"),         tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2) 
  title(main="Beta", outer=T, line=-.5, adj=3/ncol)
  
  myboxplot(as.formula(day%.%"pseudoneutid50_BA.1~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
  myboxplot(as.formula(day%.%"bindSpike_omicron~nAbBatch"),   tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2) 
  title(main="BA1-Omicron", outer=T, line=-.5, adj=5/ncol)
  
  myboxplot(as.formula(day%.%"pseudoneutid50_BA.2~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
  myboxplot(as.formula(day%.%"bindSpike_omicron~nAbBatch"),   tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2)
  title(main="BA2-Omicron", outer=T, line=-.5, adj=7/ncol)

  myboxplot(as.formula(day%.%"pseudoneutid50_BA.4.5~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
  myboxplot(as.formula(day%.%"bindSpike_omicron~nAbBatch"),     tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2)
  title(main="BA45-Omicron", outer=T, line=-.5, adj=9/ncol)
  
  title(main="Stage "%.%st%.%" NN, "%.%ifelse(.trt==1, "Vaccine", "Placebo")%.%" Arm, "%.%day, outer=T, line=.5)
}

# put 3 days side by side
make.boxplots.1=function(st, .trt, marker.pair){
  
  tmp=subset(dat_mapped, Trialstage==st & Bserostatus==1 & Trt==.trt)
  # col=tmp$EventIndFirstInfectionD1+1
  
  par(mfrow=c(1,6), oma=c(0,0,3,0), mar=c(5.1, 1.1, 2.1, 1.1), mgp = c(2, 1, 0))
  
  offset=0  
  for (day in c("Day43","Day22","B")) {
    if (marker.pair==1) {
      myboxplot(as.formula(day%.%"pseudoneutid50~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
      myboxplot(as.formula(day%.%"bindSpike~nAbBatch"),      tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2) 
      
    } else if (marker.pair==2) {
      myboxplot(as.formula(day%.%"pseudoneutid50_B.1.351~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
      myboxplot(as.formula(day%.%"bindSpike_beta~nAbBatch"),         tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2) 

    } else if (marker.pair==3) {
      myboxplot(as.formula(day%.%"pseudoneutid50_BA.1~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
      myboxplot(as.formula(day%.%"bindSpike_omicron~nAbBatch"),   tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2) 
    }
    title(main=day, outer=T, line=-.75, adj=(1+offset)/6)
    offset=offset+2
  }
  
  # myboxplot(as.formula(day%.%"pseudoneutid50_BA.2~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
  # myboxplot(as.formula(day%.%"bindSpike_omicron~nAbBatch"),   tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2) 
  # title(main="BA2-Omicron", outer=T, line=-.5, adj=7/10)
  # 
  # myboxplot(as.formula(day%.%"pseudoneutid50_BA.4.5~nAbBatch"), tmp, ylim=c(0,4.5), main="ID50", xlab="nAbBatch", col=col1)
  # myboxplot(as.formula(day%.%"bindSpike_omicron~nAbBatch"),     tmp, ylim=c(0,4.5), main="bAb",  xlab="nAbBatch", col=col2) 
  # title(main="BA45-Omicron", outer=T, line=-.5, adj=9/10)
  
  if (marker.pair==1) {
    title(main="Stage "%.%st%.%" NN, "%.%ifelse(.trt==1, "Vaccine", "Placebo")%.%" Arm, "%.%"Ancestral", outer=T, line=.5)
  } else if (marker.pair==2) {
    title(main="Stage "%.%st%.%" NN, "%.%ifelse(.trt==1, "Vaccine", "Placebo")%.%" Arm, "%.%"Beta", outer=T, line=.5)
  } else if (marker.pair==3) {
    title(main="Stage "%.%st%.%" NN, "%.%ifelse(.trt==1, "Vaccine", "Placebo")%.%" Arm, "%.%"BA1-Omicron", outer=T, line=.5)
  }
}
```

```{r batch_adj_func, include=FALSE}

rank.corr=function(st, days, trts, loss=c("s","p"), ties=c("rm","none")){
  loss = match.arg(loss)
  ties = match.arg(ties)
  
  cc=seq(0,0.5,0.05)
  
  llox <- lod <- 2.612
  
  all.cors=NULL
  legends=c()
  
  for (i in 1:3) {
  for (day in days) {
      if (i==1) {
        nAb=day%.%"pseudoneutid50"; bAb=day%.%"bindSpike"} 
      else if (i==2){
        nAb=day%.%"pseudoneutid50_B.1.351"; bAb=day%.%"bindSpike_beta"
      } else if (i==3) {
        nAb=day%.%"pseudoneutid50_BA.1"; bAb=day%.%"bindSpike_omicron"
      }
      # cat (nAb, bAb, "\n")
    
      for(.trt in trts) {
        tmp=subset(dat_mapped, Trialstage==st & Bserostatus==1 & Trt==.trt & !is.na(get(nAb)) & !is.na(get(bAb)) & !is.na(nAbBatch))
        
        # par(mfrow=c(1,2), oma=c(0,0,2,0))
        # myboxplot(as.formula(nAb%.%"~nAbBatch"), tmp, ylim=c(0,4.5), main=nAb, xlab="nAbBatch", col=col)
        # myboxplot(as.formula(bAb%.%"~nAbBatch"), tmp, ylim=c(0,4.5), main=bAb, xlab="nAbBatch", col=col)
        # title(main="Stage 2 NN, "%.%ifelse(.trt==0,"Placebo","Vaccine")%.%" Arm", outer=T, line=1)
        
        # remove those nAb < lod to deal with ties
        if (ties=="rm") {
          tmp = subset(tmp, get(nAb)>log10(lod))
        } else if (ties=="none") {
          # do nothing
        } else stop("wrong ties methods")
        
        par(mfrow=c(3,3), mar=c(1.1, 1.1, 3.1, 1.1), oma=c(0,1,1,0))
        cors=sapply(cc, function(c) {
          tmp.1=tmp
          # shift batch 1 ID50 down by c 
          tmp.1[[nAb]] [tmp.1$nAbBatch==1] = tmp.1[[nAb]] [tmp.1$nAbBatch==1] - c
          # censor at lod
          tmp.1[[nAb]]  = ifelse (tmp.1[[nAb]] < log10(lod), log10(lod/2), tmp.1[[nAb]] )
          # 
          if (loss=="s") { #Spearman
            cor(tmp.1[[nAb]], tmp.1[[bAb]], method="s")
          } else if (loss=="p") { #Pearson
            cor(tmp.1[[nAb]], tmp.1[[bAb]], method="p")
          } else stop ("wrong loss function")
        })
        names(cors)=cc
        # title(main="Stage 2 NN, "%.%ifelse(.trt==0,"Placebo","Vaccine")%.%" Arm", outer=T, line=0)
        
        # cat(ifelse(.trt==1,"Vacc","Plac"), " estimated c is ", cc[which.max(cors)], ". ", sep="")
        all.cors=cbind(all.cors, c(chat=cc[which.max(cors)], cors))
        legends=c(legends, paste0(sub(day%.%"pseudoneut","",nAb)," v. ",sub(day%.%"bind","",bAb)))
      }
      # cat("\n")
  }
  }
  
  # ylim=c(0.7,0.92)
  ylim=NULL

  par(mfrow=c(1,3), mar=c(4.1, 2.1, 1.1, 0.1), oma=c(0,2,3,0), mgp = c(2, 1, 0))
  idx=1:3;   mymatplot(cc, all.cors[-1,idx], xlab="c", legend=days, col=1:3, legend.cex=1, legend.x=7, pch=idx%.%"", ylim=ylim, main=legends[idx[1]], cex.main=1)
  idx=1:3+3; mymatplot(cc, all.cors[-1,idx], xlab="c", legend=days, col=1:3, legend.cex=1, legend.x=7, pch=idx%.%"", ylim=ylim, main=legends[idx[1]], cex.main=1)
  idx=1:3+6; mymatplot(cc, all.cors[-1,idx], xlab="c", legend=days, col=1:3, legend.cex=1, legend.x=7, pch=idx%.%"", ylim=ylim, main=legends[idx[1]], cex.main=1)
  
  title(main="Stage "%.%st%.%" NN, "%.%ifelse(.trt==0,"Placebo","Vaccine"), outer=T, line=1)
  
  if (loss=="s") {
    label="Spearman correlation"
  } else if (loss=="p") {
    label="Pearson correlation"
  } else stop ("wrong method")
  
  if (ties=="rm") {
    label=paste0(label, ", <lod removed")
  } else if (ties=="none") {
    # do nothing
  }
  
  mtext(label, side = 2, line = .8, adj = .5, outer=T)

  print(all.cors, digits=3)
}
```

```{r shift_pooled_func, include=F}

shift_pooled = function(st, marker_pair=c("ancestral", "beta", "omicron1", "omicron2", "omicron45"), ties, loss="s") {
    
  marker_pair = match.arg(marker_pair)
  
  cc=seq(0,0.5,0.05)
  
  llox <- lod <- 2.612
  
  if (loss=="s") {
    label="Spearman correlation"
  } else if (loss=="p") {
    label="Pearson correlation"
  } else stop ("wrong method")
  
  if (ties=="rm") {
    label=paste0(label, ", <lod removed")
  } else if (ties=="none") {
    # do nothing
  }
  
  ### make data
  
  if (marker_pair=="ancestral") {
    nAb="pseudoneutid50"; bAb="bindSpike"
  } else if (marker_pair=="beta"){
    nAb="pseudoneutid50_B.1.351"; bAb="bindSpike_beta"
  } else if (marker_pair=="omicron1") {
    nAb="pseudoneutid50_BA.1"; bAb="bindSpike_omicron"
  } else if (marker_pair=="omicron2") {
    nAb="pseudoneutid50_BA.2"; bAb="bindSpike_omicron"
  } else if (marker_pair=="omicron45") {
    nAb="pseudoneutid50_BA.4.5"; bAb="bindSpike_omicron"
  } else stop("wrong marker_pair")
  
  all.cors=NULL
  legends=c()
  
  tmp1=subset(dat_mapped, Trialstage==st & Bserostatus==1 & !is.na(nAbBatch), select=c(Subjectid, nAbBatch, 
      get("Day43"%.%nAb), get("Day22"%.%nAb), get("B"%.%nAb)  )  )
  tmp2=subset(dat_mapped, Trialstage==st & Bserostatus==1 & !is.na(nAbBatch), select=c(Subjectid, nAbBatch, 
      get("Day43"%.%bAb), get("Day22"%.%bAb), get("B"%.%bAb)  )  )
  
  # make separate long data frames for nAb and bAb
  tmp1long = myreshapelong(tmp1, cols.to.be.stacked=c("Day43","Day22","B")%.%nAb, 
                           label.cols.to.be.stacked="time", new.col.name=nAb)
  tmp1long$time = sub(nAb, "", tmp1long$time)
  tmp2long = myreshapelong(tmp2, cols.to.be.stacked=c("Day43","Day22","B")%.%bAb, 
                           label.cols.to.be.stacked="time", new.col.name=bAb)
  tmp2long$time = sub(bAb, "", tmp2long$time)
  
  # merge bAb and nAb data frames
  tmplong = merge(subset(tmp1long, select=-id), subset(tmp2long, select=-id))
  tmplong = tmplong[complete.cases(tmplong),]
  
  # add a quartile indicator based on bindSpike
  breaks=quantile(tmplong[[bAb]])
  breaks[1] = breaks[1] - 0.1
  tmplong$quartile = as.numeric(cut(tmplong[[bAb]], breaks))
  
  if (ties=="rm") {
    # remove those nAb < lod to deal with ties  
    tmplong = subset(tmplong, get(nAb)>log10(lod))
  } else if (ties=="none") {
    # do nothing
  }
      
  # plot data by quartiles
  par(mfrow=c(2,4), oma=c(0,0,3,0), mar=c(3.1, 2.1, 2.1, 0.1), mgp = c(2, 1, 0))
  for (i in 4:1) {
    tmp.1=tmplong[tmplong$quartile==i,]
    if (ties=="rm" & (nrow(tmp.1)==0 | length(unique(tmp.1[[nAb]]))==1 | length(unique(tmp.1[[bAb]]))==1)) {
      plot.new(); text(0.5, 0.5, labels=" ", col="white") 
      plot.new(); text(0.5, 0.5, labels=" ", col="white") 
      # empty.plot() does not take up any space for some reason
    } else {
      myboxplot(get(nAb)~nAbBatch, tmp.1, ylim=c(0,4.5), main=nAb, xlab="nAbBatch", col=1, cex.main=1)
      myboxplot(get(bAb)~nAbBatch, tmp.1, ylim=c(0,4.5), main=bAb, xlab="nAbBatch", col=2, cex.main=1)
    }
  }
  title(main="Stage "%.%st%.%" NN"%.%", "%.%marker_pair, outer=T, line=1)


  
  # Estimate c using a quarter of data at a time
  par(mfrow=c(3,2), mar=c(3.1, 2.1, 1.1, 0.1), oma=c(0,2,3,0), mgp = c(2, 1, 0))
  chats=c()
  for (i in 4:(-1)) {
    if (i==0) {
      tmp.2=tmplong
    } else if (i==-1) {
      tmp.2=tmplong[tmplong$quartile==4 | tmplong$quartile==3,]
    } else {
      tmp.2=tmplong[tmplong$quartile==i,]
    }
    
    losses=sapply(cc, function(c) {
      tmp.1=tmp.2
      # shift batch 1 ID50 down by c 
      tmp.1[[nAb]] [tmp.1$nAbBatch==1] = tmp.1[[nAb]] [tmp.1$nAbBatch==1] - c
      # censor at lod
      tmp.1[[nAb]]  = ifelse (tmp.1[[nAb]] < log10(lod), log10(lod/2), tmp.1[[nAb]] )
      
      if (ties=="rm") {
        # remove those nAb < lod to deal with ties
        tmp.1 = subset(tmp.1, get(nAb)>log10(lod))
      } else if (ties=="none") {
        # do nothing
      }
      
      if (length(unique(tmp.1[[nAb]]))==1 | 
          length(unique(tmp.1[[bAb]]))==1 | 
          length(unique(tmp.1$nAbBatch))==1 | # there is only 1 batch left
          nrow(tmp.1)<50
          ) {
        return (0)
      }
      

      # compute loss 
      if (loss=="s") { #Spearman
        cor(tmp.1[[nAb]], tmp.1[[bAb]], method="s")
      } else if (loss=="p") { #Pearson
        cor(tmp.1[[nAb]], tmp.1[[bAb]], method="p")
      } else stop ("wrong loss function")
    })
    names(losses)=cc
    
    if (i==0) {
      main="All"
    } else if (i==-1) {
      main="Q4_3"
    } else {
      main="Q"%.%i
    }
    main=paste0(main, " (n=", nrow(tmp.2), ")")

    # plot losses
    plot(cc, losses, xlab="c", type="l", main=main)
    title(main="Stage "%.%st%.%" NN"%.%", "%.%marker_pair, outer=T, line=1)
    mtext(label, side = 2, line = .8, adj = .5, outer=T)
    
    chat=cc[which.max(losses)]
    #
    if (loss=="s") {
      # less than 0.4 spearman, chat is disregarded
      if (max(losses,na.rm=T)<0.4) chat=NA
    }
    chats=c(chats, chat)
  }  
  cat("chat: "); print(chats)
  chats
}
```


# Methods

We propose a rank-based procedure for batch adjustment. The basic idea is find a transformation for the batch 1 nAb readouts so that when they are mixed with batch 2 nAb readouts and rank together, the ranking is consistent with the ranking of the corresponding bAb. 

Let f(x) be the mapping/correction we will apply to batch 1 nAb. The choice of f(x) is not too important for now - let's just assume it is a truncated linear shift: f(x)=x-c if x-c>=lod, otherwise lod/2. We can solve an optimization problem, 

$\hat{c} = argmin_c L(rank_{bAb}, rank_{nAb}(c)),$

where $rank_{bAb}$ is the rank of each ptid in bAb for all ptids. $rank_{nAb}$ is defined similarly based on nAb. It is obviously a function of c. The loss function $L$ can be L1 norm of the difference or 1 - Spearman correlation coefficient. Optimization can be done by exhaustive search on a grid of candidate values for c.

Appendix contains two experiments that show under conditions we expect no batch effects, $\hat{c}$ is 0 and the variability is around $\pm 0.05$ or 12\%.

**Ties** Ties occur when values dip below LOD. Different methods for handling ties could have a large impact on the results when a large portion of readouts are under LOD. We take two approaches 1) keep all samples, 2) remove samples with nAb below LOD

Some details:

* If there is only one batch, or if there are less than 50 samples, or if there is only one unique nAb or bAb value, Spearman cc is set to 0.
* If Spearman cc is used as loss, then if the maximum Spearman cc is less than 0.4, $\hat{c}$ is set to NA.
* We impute BA4.5 from BA.1 and BA.2, which is missing for many ptids in stage 1 before doing batch correction.

In the following, we perform batch correction in two ways. Both ways perform batch correction separately for each marker pair (bAb Omicron is used against three ID50s: BA.1, BA.2, BA4.5) and each trial. The diference is that the first way is done separately within each treatment arm and each time point, while the second way pools over treatment arms and time points, but is done within each quartile of marker distribution. The second approach is preferrable because it is more likely that different adjustment is needed for different marker levels regardless of the treatment arm and time point that samples are from. In the second approach, we recommend $\hat{c}$ esimated using both Q4 and Q3 data.

Estimated $\hat{c}$ are shown in Section 3.3.

For most ptids, all three time points (B, D22 and D43) are in the same batch, but the following 7 ptids are the exceptions. This can be handled in the dataset construction in shift_pooled.

Batch 2
     Unique.Subject.Identifier Bleed timepoint
957      VAT008-170-0003-11007     2       D22
1352     VAT008-288-0001-11353     2       D22
2036     VAT008-356-0005-10209     3       D43
2346     VAT008-840-0011-10001     3       D43
2389     VAT008-840-0012-16001  002A       D22
2669     VAT008-840-0017-11002     3       D43
2671     VAT008-840-0017-11005     3       D43

Batch 1
     Unique.Subject.Identifier Bleed timepoint
76       VAT008-170-0003-11007  0001         B
77       VAT008-170-0003-11007  0003       D43
245      VAT008-288-0001-11353  0001         B
246      VAT008-288-0001-11353  0003       D43
770      VAT008-356-0005-10209  0001         B
771      VAT008-356-0005-10209  0002       D22
997      VAT008-840-0011-10001  0001         B
998      VAT008-840-0011-10001  0002       D22
1005     VAT008-840-0012-16001  001A         B
1006     VAT008-840-0012-16001  003A       D43
1031     VAT008-840-0017-11002  0001         B
1032     VAT008-840-0017-11005  0002       D22



# Calibration done separately within treatment arms and time points

The bAb levels between the two batches may be similar in vaccine (likely due to saturation), but not in placebo.


\newpage
## Stage 2 NN, Vaccine

```{r,echo=F,fig.height=3}
make.boxplots.1(st=2, .trt=1, marker.pair=1)
```

\vspace{10pt}

```{r,echo=F,fig.height=3}
make.boxplots.1(st=2, .trt=1, marker.pair=2)
```

\vspace{10pt}

```{r,echo=F,fig.height=3}
make.boxplots.1(st=2, .trt=1, marker.pair=3)
```


```{r,echo=F}
rank.corr(st=2, c("Day43","Day22","B"), trts=1, loss="s", ties="none")
rank.corr(st=2, c("Day43","Day22","B"), trts=1, loss="s", ties="rm")
```


\newpage
## Stage 2 NN, Placebo

```{r,echo=F,fig.height=3}
make.boxplots.1(st=2, .trt=0, marker.pair=1)
```

\vspace{10pt}

```{r,echo=F,fig.height=3}
make.boxplots.1(st=2, .trt=0, marker.pair=2)
```

\vspace{10pt}

```{r,echo=F,fig.height=3}
make.boxplots.1(st=2, .trt=0, marker.pair=3)
```



```{r,echo=F}
rank.corr(st=2, c("Day43","Day22","B"), trts=0, loss="p", ties="none")
rank.corr(st=2, c("Day43","Day22","B"), trts=0, loss="p", ties="rm")
```




\newpage
## Stage 1 NN, Vaccine

```{r,echo=F,fig.height=3}
make.boxplots.1(st=1, .trt=1, marker.pair=1)
```

\vspace{10pt}

```{r,echo=F,fig.height=3}
make.boxplots.1(st=1, .trt=1, marker.pair=2)
```

\vspace{10pt}

```{r,echo=F,fig.height=3}
make.boxplots.1(st=1, .trt=1, marker.pair=3)
```


```{r,echo=F}
rank.corr(st=1, c("Day43","Day22","B"), trts=1, loss="p", ties="none")
rank.corr(st=1, c("Day43","Day22","B"), trts=1, loss="p", ties="rm")
```


\newpage
## Stage 1 NN, Placebo

```{r,echo=F,fig.height=3}
make.boxplots.1(st=1, .trt=0, marker.pair=1)
```

\vspace{10pt}

```{r,echo=F,fig.height=3}
make.boxplots.1(st=1, .trt=0, marker.pair=2)
```

\vspace{10pt}

```{r,echo=F,fig.height=3}
make.boxplots.1(st=1, .trt=0, marker.pair=3)
```


```{r,echo=F}
rank.corr(st=1, c("Day43","Day22","B"), trts=0, loss="p", ties="none")
rank.corr(st=1, c("Day43","Day22","B"), trts=0, loss="p", ties="rm")
```


\newpage
# Calibration done separately within marker quartiles

The idea is to pool over different time points and treatment arms, but keep it separate for different marker pairs. After pooling, there are more data and we can divide into four quartiles based on marker level.



## Stage 2 NN

\newpage
```{r, echo=F}
res.st2=cbind(
  shift_pooled (st=2, marker_pair="ancestral", ties="none"),
  shift_pooled (st=2, marker_pair="ancestral", ties="rm"),
  shift_pooled (st=2, marker_pair="beta", ties="none"),
  shift_pooled (st=2, marker_pair="beta", ties="rm"),
  shift_pooled (st=2, marker_pair="omicron1", ties="none"),
  shift_pooled (st=2, marker_pair="omicron1", ties="rm"),
  shift_pooled (st=2, marker_pair="omicron2", ties="none"),
  shift_pooled (st=2, marker_pair="omicron2", ties="rm"),
  shift_pooled (st=2, marker_pair="omicron45", ties="none"),
  shift_pooled (st=2, marker_pair="omicron45", ties="rm")
)
```


## Stage 1 NN

\newpage
```{r, echo=F}
res.st1=cbind(
  shift_pooled (st=1, marker_pair="ancestral", ties="none"),
  shift_pooled (st=1, marker_pair="ancestral", ties="rm"),
  shift_pooled (st=1, marker_pair="beta", ties="none"),
  shift_pooled (st=1, marker_pair="beta", ties="rm"),
  shift_pooled (st=1, marker_pair="omicron1", ties="none"),
  shift_pooled (st=1, marker_pair="omicron1", ties="rm"),
  shift_pooled (st=1, marker_pair="omicron2", ties="none"),
  shift_pooled (st=1, marker_pair="omicron2", ties="rm"),
  shift_pooled (st=1, marker_pair="omicron45", ties="none"),
  shift_pooled (st=1, marker_pair="omicron45", ties="rm")
)
```


## Estimated c

Results for stage 2
```{r, echo=F}
# pick rm, which are the even columns
tab = t(res.st2[,seq(2,10,2)])
rownames(tab)=c("ancestral","beta","omicron1","omicron2","omicron45")
colnames(tab)=c("Q"%.%4:1, "All", "Q4_3")
tab
```

Results for stage 1
```{r, echo=F}
# pick rm
tab = t(res.st1[,seq(2,10,2)])
rownames(tab)=c("ancestral","beta","omicron1","omicron2","omicron45")
colnames(tab)=c("Q"%.%4:1, "All", "Q4_3")
tab
```
\newpage
# Appendix


## Negative control experiment I

We test the procedure on two bAb readouts. Since there are no batch effects for bAb, the truth $c$ is 0. $\hat{c}$s are between -0.05 and 0.05.


```{r,echo=F}
cc=seq(-0.2,0.2,0.05)

all.cors=NULL
legends=c()
for (i in 1:3) {
  if (i==1) {
    nAb="Day43bindSpike_beta"; bAb="Day43bindSpike"
  } else if (i==2){
    nAb="Day43bindSpike_omicron"; bAb="Day43bindSpike"
  } else if (i==3) {
    nAb="Day43bindSpike_beta"; bAb="Day43bindSpike_omicron"
  }
  cat (nAb, bAb, "\n")

  for(.trt in 0:1) {
    myprint(.trt)
    tmp=subset(dat_mapped, Trialstage==2 & Bserostatus==1 & Trt==.trt & !is.na(get(nAb)) & !is.na(get(bAb)) & !is.na(nAbBatch))
    col=tmp$EventIndFirstInfectionD1+1

    # par(mfrow=c(1,2), oma=c(0,0,2,0))
    # myboxplot(as.formula(nAb%.%"~nAbBatch"), tmp, ylim=c(0,4.5), main=nAb, xlab="nAbBatch", col=col)
    # myboxplot(as.formula(bAb%.%"~nAbBatch"), tmp, ylim=c(0,4.5), main=bAb, xlab="nAbBatch", col=col)
    # title(main="Stage 2 NN, "%.%ifelse(.trt==0,"Placebo","Vaccine")%.%" Arm", outer=T, line=1)
  
    llox=min(tmp[[nAb]])
    
    par(mfrow=c(3,3), mar=c(1.1, 1.1, 3.1, 1.1), oma=c(0,1,2,0))
    cors=sapply(cc, function(c) {
      tmp.1=tmp
      # shift batch 1 ID50 down by c but not lower than llox
      tmp.1[[nAb]] [tmp.1$nAbBatch==1] = tmp.1[[nAb]] [tmp.1$nAbBatch==1] - c
      tmp.1[[nAb]]  = ifelse (tmp.1[[nAb]] <llox, llox, tmp.1[[nAb]] )
      ranks = cbind(id50=rank(tmp.1[[nAb]] ), bind=rank(tmp.1[[bAb]] ))
      # corplot(ranks[,"bind"], ranks[,"id50"], main=c, method="s", digit.cor=3)
      cor(ranks[,"bind"], ranks[,"id50"], method="s")
    })
    names(cors)=cc
    # title(main="Stage 2 NN, "%.%ifelse(.trt==0,"Placebo","Vaccine")%.%" Arm", outer=T, line=0)
    
    cat("Estimated c is ", cc[which.max(cors)], ".\n", sep="")
    all.cors=cbind(all.cors, cors)
    legends=c(legends, paste0(sub("Day43","",nAb)," v. ",sub("Day43","",bAb), ", ", ifelse(.trt==0,"Plac","Vacc")))
  }
}

# ylim=c(0.7,0.92)
ylim=NULL
par(mfrow=c(1,2), mar=c(5.1, 3.1, 0.1, 0.1), oma=c(0,1,3,0))
mymatplot(cc, all.cors[,c(1,3,5)],   xlab="c", ylab="Spearman correlation", legend=legends[c(1,3,5)],   col=1:3, legend.cex=.75, legend.x=7, pch=c("1","3","5"), ylim=ylim)
mymatplot(cc, all.cors[,c(1,3,5)+1], xlab="c", ylab="Spearman correlation", legend=legends[c(1,3,5)+1], col=1:3, legend.cex=.75, legend.x=7, pch=c("2","4","6"), ylim=ylim)
title(main="Stage 2 NN, Spearman correlation", outer=T, line=0.5)

print(all.cors)

```




## Negative control experiment II

We permute the nAbBatch value so that there are no batch effects. Again, $\hat{c}$s are between -0.05 and 0.05.


```{r,echo=F}

# centerend around 0
cc=seq(-0.2,0.2,0.05)

all.cors=NULL
legends=c()
for (i in 1:3) {
  if (i==1) {
    nAb="Day43pseudoneutid50";         bAb="Day43bindSpike"} 
  else if (i==2){
    nAb="Day43pseudoneutid50_B.1.351"; bAb="Day43bindSpike_beta"
  } else if (i==3) {
    nAb="Day43pseudoneutid50_BA.1";    bAb="Day43bindSpike_omicron"
  }
  cat (nAb, bAb, "\n")

  for(.trt in 0:1) {
    myprint(.trt)
    tmp=subset(dat_mapped, Trialstage==2 & Bserostatus==1 & Trt==.trt & !is.na(get(nAb)) & !is.na(get(bAb)) & !is.na(nAbBatch))
    col=tmp$EventIndFirstInfectionD1+1

    tmp$nAbBatch = sample(tmp$nAbBatch)
    
    # par(mfrow=c(1,2), oma=c(0,0,2,0))
    # myboxplot(as.formula(nAb%.%"~nAbBatch"), tmp, ylim=c(0,4.5), main=nAb, xlab="nAbBatch", col=col)
    # myboxplot(as.formula(bAb%.%"~nAbBatch"), tmp, ylim=c(0,4.5), main=bAb, xlab="nAbBatch", col=col)
    # title(main="Stage 2 NN, "%.%ifelse(.trt==0,"Placebo","Vaccine")%.%" Arm", outer=T, line=1)
  
    llox=min(tmp[[nAb]])
    
    par(mfrow=c(3,3), mar=c(1.1, 1.1, 3.1, 1.1), oma=c(0,1,2,0))
    cors=sapply(cc, function(c) {
      tmp.1=tmp
      # shift batch 1 ID50 down by c but not lower than llox
      tmp.1[[nAb]] [tmp.1$nAbBatch==1] = tmp.1[[nAb]] [tmp.1$nAbBatch==1] - c
      tmp.1[[nAb]]  = ifelse (tmp.1[[nAb]] <llox, llox, tmp.1[[nAb]] )
      ranks = cbind(id50=rank(tmp.1[[nAb]] ), bind=rank(tmp.1[[bAb]] ))
      # corplot(ranks[,"bind"], ranks[,"id50"], main=c, method="s", digit.cor=3)
      cor(ranks[,"bind"], ranks[,"id50"], method="s")
    })
    names(cors)=cc
    # title(main="Stage 2 NN, "%.%ifelse(.trt==0,"Placebo","Vaccine")%.%" Arm", outer=T, line=0)
    
    cat("Estimated c is ", cc[which.max(cors)], ".\n", sep="")
    all.cors=cbind(all.cors, cors)
    legends=c(legends, paste0(sub("Day43pseudoneut","",nAb)," v. ",sub("Day43","",bAb), ", ", ifelse(.trt==0,"Plac","Vacc")))
  }
}

# ylim=c(0.7,0.92)
ylim=NULL
par(mfrow=c(1,2), mar=c(5.1, 3.1, 0.1, 0.1), oma=c(0,1,3,0))
mymatplot(cc, all.cors[,c(1,3,5)],   xlab="c", ylab="Spearman correlation", legend=legends[c(1,3,5)],   col=1:3, legend.cex=.75, legend.x=7, pch=c("1","3","5"), ylim=ylim)
mymatplot(cc, all.cors[,c(1,3,5)+1], xlab="c", ylab="Spearman correlation", legend=legends[c(1,3,5)+1], col=1:3, legend.cex=.75, legend.x=7, pch=c("2","4","6"), ylim=ylim)
title(main="Stage 2 NN, Spearman correlation", outer=T, line=0.5)

print(all.cors)

```

