---
header-includes:
  - \usepackage{float}
output:
  pdf_document: default
html_document: default
citation_package: natbib
number_sections: true
extra_dependencies: ["caption", "subcaption", "graphicx"]
toc: true
---

# Baseline Risk Score (Proxy for SARS-CoV-2 Exposure) {#baseline-riskscore}

```{r riskVarstable, warning=FALSE, echo=FALSE, message=FALSE}
library(tidyverse, quietly = T)
library(kableExtra, quietly = T)
library(conflicted, quietly = T)
conflicted::conflict_prefer("filter", "dplyr")
conflict_prefer("summarise", "dplyr")
load(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "objects_for_running_SL.rda"))
source(here("riskscore_baseline", "code", "study_specific_functions.R"))

study_name_code <- studyName_for_report

### create footnotes ###
dropped.riskVars.fewer.0s1s <- read.table(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "drop_riskVars_with_fewer_0s_or_1s.csv")) %>%
  separate(V1, c("droppedVars"), sep = " ") %>%
  .$droppedVars %>%
  paste(collapse=", ") 

if(dropped.riskVars.fewer.0s1s == "No"){
  footnote1 <- "1. All binary input variables had >3 cases in the variable = 1 or 0 subgroup."
  eval.footnote1.table = FALSE
}else{
  footnote1 <- paste0("1. Binary input variable/s ", paste(unlist(strsplit(dropped.riskVars.fewer.0s1s, ",")), collapse = ", "), " had <= 3 cases in the variable = 1 or 0 subgroup and dropped from analysis.")
  eval.footnote1.table = TRUE
}

dropped.riskVars.high.NAs <- read.table(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "drop_riskVars_with_high_total_missing_values.csv")) %>%
  separate(V1, c("droppedVars"), sep = " ") %>%
  .$droppedVars %>%
  paste(collapse=", ") 

if(dropped.riskVars.high.NAs == "No"){
  footnote2 <- "2. No input variable had more than 5% missing values."
  eval.footnote2.table = FALSE
}else{
  footnote2 <- paste0("2. ", dropped.riskVars.high.NAs, " had more than 5% missing values and dropped from analysis.")
  eval.footnote2.table = TRUE
}
  
vars.with.imputed.values <- read.table(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "impute_missing_values.csv")) %>%
  separate(V1, c("delete", "imputedVars"), sep = ": ") %>%
  .$imputedVars %>%
  paste(collapse=", ") 
  
if(vars.with.imputed.values == "None"){
  footnote3 <- "3. No variable had less than 5% missing values to activate imputation."
  eval.footnote3.table = FALSE
}else{
  footnote3 <- paste0("3. ", vars.with.imputed.values, " had less than 5% missing values. The missing values were imputed using the mice package in R.")
  eval.footnote3.table = TRUE
}

if(studyName_for_report == "PREVENT19"){
  footnote4 <- paste0("4. Baseline risk score development is restricted to only US subjects.")
  eval.footnote4.table = TRUE
}
#########################

if(studyName_for_report %in% c("COVE", "MockCOVE")){
  day = "Day 57"
  start = "7 days"
}
if(studyName_for_report %in% c("ENSEMBLE", "MockENSEMBLE")){
  day = "Day 29"
  start = "1 day"
}
if(studyName_for_report == "PREVENT19"){
  day = "Day 35"
  start = "1 day"
}
if(studyName_for_report == "COV002"){
  day = "Day 57"
  start = "7 days"
}

caption <- "Individual baseline variables in baseline SARS-CoV-2 negative per-protocol placebo recipients that were used in the Superlearner model for developing risk score and predicting occurrence of COVID-19."

tab <- read.csv(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "risk_vars.csv"), row.names = 1,
         header = TRUE) %>%
  kable(
    #format = output_type,
    booktabs = TRUE,
    linesep = "",
    caption = caption,
    longtable = T
  ) %>%
  column_spec(2, width = "8cm") %>%
  column_spec(4, width = "2cm") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"),
                font_size = 8)

if(studyName_for_report %in% c("ENSEMBLE")){
  tab <- tab %>% 
    footnote(c(footnote1,
               footnote2,
               footnote3),
             threeparttable = TRUE)
}

if(studyName_for_report %in% c("PREVENT19")){
  tab <- tab %>% 
    footnote(c(footnote1,
               footnote2,
               footnote3,
               footnote4),
             threeparttable = TRUE)
}

tab
rm(tab)
  
```



<!-- \clearpage -->

<!-- ```{r footnote1-table, warning=FALSE, echo=FALSE, eval = eval.footnote1.table} -->
<!-- caption <- "Binary input variable/s having <= 3 cases in the variable = 1 or 0 subgroup and dropped from analysis (sorted by number of cases in Variable = 1 subgroup)." -->

<!-- tab1 <- inputFile %>% -->
<!--   filter(Riskscorecohortflag == 1 & Trt == 0) %>% -->
<!--   select(Ptid, Trt, all_of(endpoint), all_of(all_risk_vars)) %>% -->
<!--   drop_na(Ptid, Trt, all_of(endpoint)) -->

<!-- tab2 <- tab1 %>% -->
<!--   select(all_of(all_risk_vars)) %>% -->
<!--   map(~ sum(is.na(.))) %>% -->
<!--   as.data.frame() %>% -->
<!--   t() %>% -->
<!--   as.data.frame() %>% -->
<!--   tibble::rownames_to_column(var = "Variable Name") %>% -->
<!--   get_defs_comments_riskVars()  -->

<!-- tab3 <- inputFile %>% -->
<!--   filter(Riskscorecohortflag == 1 & Trt == 0) %>% -->
<!--   drop_na(Ptid, Trt, all_of(endpoint)) %>% -->
<!--   #select(c(Ptid, strsplit(dropped.riskVars.fewer.0s1s, ", ")[[1]], all_of(endpoint))) %>% -->
<!--   select(c(Ptid, all_of(all_risk_vars), all_of(endpoint))) %>% -->
<!--   select(-c("Age", "BMI")) %>% # keep only binary variables -->
<!--   mutate(EventIndPrimaryIncludeNotMolecConfirmedD29 = ifelse(EventIndPrimaryIncludeNotMolecConfirmedD29 == 0, "Non-Case", "Case")) %>% -->
<!--   pivot_longer(!c(Ptid, all_of(endpoint)), names_to = "Variable Name", values_to = "value")  -->

<!-- tab4 <- tab3 %>% -->
<!--   group_by(`Variable Name`, value) %>% -->
<!--   count() %>% -->
<!--   pivot_wider(names_from = "value", values_from = "n") %>% -->
<!--   rename(`Variable = 0 subgroup` = `0`, -->
<!--          `Variable = 1 subgroup` = `1`)  -->

<!-- tab5 <- tab3 %>% -->
<!--   group_by(`Variable Name`, value, EventIndPrimaryIncludeNotMolecConfirmedD29) %>% -->
<!--   count() %>% -->
<!--   pivot_wider(names_from = "value", values_from = "n") %>% -->
<!--   filter(EventIndPrimaryIncludeNotMolecConfirmedD29 == "Case") %>% -->
<!--   mutate(`1` = ifelse(is.na(`1`), 0, `1`)) %>% -->
<!--   rename(`Cases in variable = 0 subgroup` = `0`, -->
<!--          `Cases in variable = 1 subgroup` = `1`) %>% -->
<!--   ungroup() -->

<!-- tab6 <- tab4 %>% left_join(tab5 %>% select(-EventIndPrimaryIncludeNotMolecConfirmedD29), by = "Variable Name") %>% -->
<!--   mutate(`Variable = 0 subgroup N (cases)` = paste0(`Variable = 0 subgroup`, " (", `Cases in variable = 0 subgroup`, ")"), -->
<!--          `Variable = 1 subgroup N (cases)` = paste0(`Variable = 1 subgroup`, " (", `Cases in variable = 1 subgroup`, ")")) %>% -->
<!--   left_join(tab2 %>% select(`Variable Name`, Definition), by = "Variable Name") %>% -->
<!--   arrange(desc(`Cases in variable = 1 subgroup`)) %>% -->
<!--   filter(`Cases in variable = 0 subgroup` <= 3 | `Cases in variable = 1 subgroup` <= 3) %>% -->
<!--   select(`Variable Name`, Definition, `Variable = 0 subgroup N (cases)`, `Variable = 1 subgroup N (cases)`) -->

<!-- tab6 %>%  -->
<!--   select(`Variable Name`, Definition, everything()) %>% -->
<!--   kable(escape = F, -->
<!--     booktabs = TRUE, -->
<!--     linesep = "", -->
<!--     caption = caption, -->
<!--     col.names = linebreak(c("Variable\nName", "Definition", "Variable = 0 subgroup \n N (cases)", "Variable = 1 subgroup \n N (cases)"), align = "c") -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("hold_position"), -->
<!--                 font_size = 8) %>% -->
<!--   column_spec(1:2, width = "5cm") %>% -->
<!--   column_spec(3:4, width = "3cm") %>% -->
<!--   row_spec(0,bold=TRUE) %>% -->
<!--   collapse_rows(columns = 1, valign = "top", latex_hline = "major")  -->

<!-- rm(tab1, tab2, tab3, tab4, tab5, tab6) -->

<!-- ``` -->




<!-- ```{r footnote2-table, warning=FALSE, echo=FALSE, eval = eval.footnote2.table} -->
<!-- caption <- "Input variable/s dropped from analysis for having more than 5% missing values." -->

<!-- dat <- inputFile %>% -->
<!--   filter(Riskscorecohortflag == 1 & Trt == 0) %>% -->
<!--   select(all_of(all_risk_vars))  -->

<!-- inputFile %>% -->
<!--   filter(Riskscorecohortflag == 1 & Trt == 0) %>% -->
<!--   map(~ sum(is.na(.))) %>% -->
<!--   as.data.frame() %>% -->
<!--   t() %>% -->
<!--   as.data.frame() %>% -->
<!--   tibble::rownames_to_column(var = "Variable Name") %>% -->
<!--   mutate(V1 = paste0(V1, "/", nrow(dat), " (", format(round((V1 / nrow(dat)) * 100, 1), nsmall = 1), "%)")) %>% -->
<!--   get_defs_comments_riskVars() %>% -->
<!--   filter(`Variable Name` %in% strsplit(dropped.riskVars.high.NAs, ", ")[[1]]) %>% -->
<!--   rename(`Total missing values` = V1) %>% -->
<!--   select(`Variable Name`, Definition, `Total missing values`, Comments) %>% -->
<!--   kable( -->
<!--     booktabs = TRUE, -->
<!--     linesep = "", -->
<!--     caption = caption -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("hold_position"), -->
<!--                 font_size = 8) %>% -->
<!--   column_spec(1:2, width = "5cm") %>% -->
<!--   row_spec(0,bold=TRUE) %>% -->
<!--   collapse_rows(columns = 1, valign = "top", latex_hline = "major") -->

<!-- rm(dat) -->

<!-- ``` -->




<!-- ```{r footnote3-table, warning=FALSE, echo=FALSE, eval = eval.footnote3.table} -->
<!-- caption <- "Input variable/s having less than 5\\% missing values. The missing values were imputed using the mice package in R." -->

<!-- dat <- inputFile %>% -->
<!--   filter(Riskscorecohortflag == 1 & Trt == 0) %>% -->
<!--   select(all_of(all_risk_vars))  -->

<!-- inputFile %>% -->
<!--   filter(Riskscorecohortflag == 1 & Trt == 0) %>% -->
<!--   map(~ sum(is.na(.))) %>% -->
<!--   as.data.frame() %>% -->
<!--   t() %>% -->
<!--   as.data.frame() %>% -->
<!--   tibble::rownames_to_column(var = "Variable Name") %>% -->
<!--   mutate(V1 = paste0(V1, "/", nrow(dat), " (", format(round((V1 / nrow(dat)) * 100, 1), nsmall = 1), "%)")) %>% -->
<!--   get_defs_comments_riskVars() %>% -->
<!--   filter(`Variable Name` %in% strsplit(vars.with.imputed.values, ", ")[[1]]) %>% -->
<!--   rename(`Total missing values` = V1) %>% -->
<!--   select(`Variable Name`, Definition, `Total missing values`, Comments) %>% -->
<!--   mutate(Comments = "NA") %>% -->
<!--   kable( -->
<!--     booktabs = TRUE, -->
<!--     linesep = "", -->
<!--     caption = caption -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("hold_position"), -->
<!--                 font_size = 8) %>% -->
<!--   column_spec(1:2, width = "5cm") %>% -->
<!--   row_spec(0,bold=TRUE) %>% -->
<!--   collapse_rows(columns = 1, valign = "top", latex_hline = "major") -->

<!-- rm(dat) -->

<!-- ``` -->

\clearpage

```{r learner-screens, warning=FALSE, echo=FALSE}
caption <- "All learner-screen combinations (14 in total) used as input to the Superlearner."

read.csv(here::here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "learner-screens.csv"),
         row.names = 1, header = TRUE) %>%
  rename(`Screen*` = `Screen.`) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  column_spec(1:2, width = "5cm") %>%
  row_spec(0,bold=TRUE) %>%
  collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
  footnote(c("*Screen details:",
             "all: includes all variables",
             "glmnet: includes variables with non-zero coefficients in the standard implementation of SL.glmnet that optimizes the lasso tuning parameter via cross-validation",
             "univar_logistic_pval: Wald test 2-sided p-value in a logistic regression model < 0.10",
             "highcor_random: if pairs of quantitative variables with Spearman rank correlation > 0.90, select one of the variables at random"),
           threeparttable = TRUE)

```




```{r cvsl-args, warning=FALSE, echo=FALSE}
caption <- "Arguments supplied to CV.Superlearner."

cvsl_args <- read.csv(here::here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "cvsl_args.csv"),
         row.names = 1, header = TRUE) 

cases_placebo <- cvsl_args %>% filter(Argument == "Cases/Total Subjects in placebo group (%)") 

cvsl_args %>%
  filter(Argument != "Cases/Total Subjects in placebo group (%)") %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  row_spec(0,bold=TRUE) %>%
  #column_spec(1:2, width = "5cm") %>%
  # collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
  footnote(paste0(cases_placebo$Argument, " = ", cases_placebo$Value),
           threeparttable = TRUE)

```

\begin{landscape}
\clearpage



```{r, echo=FALSE, out.width="99%", out.height="120%", fig.cap= paste0("Cross-validated AUC (95\\% CI) of algorithms for predicting COVID-19 disease status starting ", start, " after ", day, ". CV-AUCs were computed using only data from the placebo arm.")}
knitr::include_graphics(here::here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "risk_placebo_cvaucs.png"))
```

\end{landscape}


```{r, echo=FALSE, out.height="94%", fig.cap=paste0("CV-estimated predicted probabilities of COVID-19 disease ", start, " after ", day, " by case/control status for top 2 learners, SuperLearner and Discrete SL. CV-estimated predicted probabilities were computed using only data from the placebo arm.")}
knitr::include_graphics(here::here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "predProb_riskscore_plac.png"))
```

\clearpage


```{r, echo=FALSE, out.width="95%", out.height="95%", fig.cap="ROC curves based off CV-estimated predicted probabilities for the top 2 learners, Superlearner and Discrete SL. CV-estimated predicted probabilities were computed using only data from the placebo arm."}
knitr::include_graphics(here::here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "ROCcurve_riskscore_plac.png"))
```

\clearpage

```{r risk-sl-weights, warning=FALSE, echo=FALSE}
caption <- "Weights assigned by Superlearner."
read.csv(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "SL_weights.csv"), row.names = 1,
         header = TRUE) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  row_spec(0,bold=TRUE)
```

\begin{landscape}
\clearpage

```{r SLtopmodels, warning=FALSE, echo=FALSE}
caption <- "Learners assigned weight > 0.0 by Superlearner sorted by weight. Predictors within each learner are sorted by variable importance which is the absolute value in Coefficient (in case of learners like SL.glm, SL.gam, SL.glm.interaction), or Gain (in case of SL.xgboost) or Importance (in case of SL.ranger.imp)."

read.csv(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "SL_all_models_with_predictors.csv"),
         row.names = 1, header = TRUE) %>%
  mutate(Gain = if("Gain" %in% colnames(.)) as.numeric(Gain) else NULL,
        Importance = if("Importance" %in% colnames(.)) as.numeric(Importance) else NULL,
        Coefficient = if("Coefficient" %in% colnames(.)) as.numeric(Coefficient) else NULL) %>%
  arrange( if("Weight" %in% colnames(.)) desc(Weight) else NULL,
           if("Gain" %in% colnames(.)) desc(abs(Gain)) else NULL,
           if("Importance" %in% colnames(.)) desc(abs(Importance)) else NULL,
           if("Coefficient" %in% colnames(.)) desc(abs(Coefficient)) else NULL) %>%
  filter(Weight > 0.0) %>%
  mutate(across(.cols = everything(), ~gsub(" ", "", ., fixed = TRUE))) %>%
  mutate(across(.cols = everything(), ~na_if(., "NA"))) %>%
  select_if(~sum(!is.na(.)) > 0) %>%
  kable(
    longtable = T,
    booktabs = TRUE,
    linesep = "",
    caption = caption
  ) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"),
                font_size = 5) %>%
  row_spec(0,bold=TRUE)

```
\end{landscape}


```{r, echo=FALSE, out.width="100%", out.height="90%", fig.cap=paste0("Superlearner predicted probabilities of COVID-19 disease in vaccinees ", start, " after ", day, " by case/control status.")}
knitr::include_graphics(here::here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "predProb_riskscore_vacc_onlySL.png"))
```

\clearpage


```{r, echo=FALSE, out.width="95%", out.height="95%", fig.cap="ROC curve based off Superlearner predicted probabilities in vaccinees."}
knitr::include_graphics(here::here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "ROCcurve_riskscore_vacc_onlySL.png"))
```

\clearpage

## Analysis details towards deriving baseline risk score

The Baseline Risk Score analysis is conducted in baseline SARS-CoV-2 sero-negative per-protocol participants. The analysis considers the following as input:

1. data_processed.csv file (created by the data processing step)

2. Riskscorecohortflag (created by the data processing step): This flag identifies the subjects from both arms (placebo and vaccine) that are to be considered for risk score analysis. So, all subjects with Riskscorecohortflag == 1 have a risk score.

3. Risk score variables (shown in Table 1)

4. Endpoint: The endpoint used is `r endpoint`

Tables 5, 6 and 7 (below) show the number of subjects by study arm and endpoint status in the data before applying the Riskscorecohortflag, after applying the Riskscorecohortflag and after conducting the risk score analysis, respectively. 

The risk score analysis code appends two columns (risk_score and standardized_risk_score) to the data_processed.csv file and drops out subjects that do not have a risk score (thus keeps only subjects with Riskscorecohortflag == 1 and no missing value for the endpoint). 

```{r cases-beforeRiskscorecohortFLAG, warning=FALSE, echo=FALSE, message=FALSE}
caption <- "Cases per treatment arm in data\\_processed.csv before applying RiskscorecohortFLAG."
new_colnames = c("Non-Cases", paste0("Post-", day, "-Cases"))

read.csv(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "cases_prior_to_applying_Riskscorecohortflag.csv"), row.names = 1,
         header = TRUE) %>%
  tibble::rownames_to_column(var = "Study-Arm") %>%
  rename_with(~new_colnames, c("X0", "X1")) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  footnote(c(paste0("Post-Day ", day, " Cases: COVID-19 primary endpoints that occur at least ", start, " after the ", day, " visit.")),
             threeparttable = TRUE)

```



```{r cases-prior, warning=FALSE, echo=FALSE, message=FALSE}
caption <- "Cases per treatment arm after applying RiskscorecohortFLAG (prior to risk score analysis)."
new_colnames = c("Non-Cases", paste0("Post-", day, "-Cases"))

read.csv(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "cases_prior_riskScoreAnalysis.csv"), row.names = 1,
         header = TRUE) %>%
  tibble::rownames_to_column(var = "Study-Arm") %>%
  rename_with(~new_colnames, c("X0", "X1")) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  footnote(c(paste0("Post-Day ", day, " Cases: COVID-19 primary endpoints that occur at least ", start, " after the ", day, " visit.")),
             threeparttable = TRUE)

```


```{r cases-post-riskScore, warning=FALSE, echo=FALSE, message=FALSE}
caption <- "Cases per treatment arm post risk score analysis."

read.csv(here("riskscore_baseline", "output", Sys.getenv("TRIAL"), "cases_post_riskScoreAnalysis.csv"), row.names = 1,
         header = TRUE) %>%
  tibble::rownames_to_column(var = "Study-Arm") %>%
  rename_with(~new_colnames, c("X0", "X1")) %>%
  kable(
    booktabs = TRUE,
    linesep = "",
    caption = caption) %>%
  kable_styling(latex_options = c("hold_position"),
                font_size = 9) %>%
  footnote(c(paste0("Post-Day ", day, " Cases: COVID-19 primary endpoints that occur at least ", start, " after the ", day, " visit.")),
             threeparttable = TRUE)

```

<!-- \clearpage -->

<!-- ## Superlearner details  -->


<!-- ```{r cvsl-details, warning=FALSE, echo=FALSE, message=FALSE} -->
<!-- caption <- "Arguments provided to CV-Superlearner function." -->

<!-- read.csv(here("riskscore_baseline", "output", "cases_post_riskScoreAnalysis.csv"), row.names = 1, -->
<!--          header = TRUE) %>% -->
<!--   tibble::rownames_to_column(var = "Study-Arm") %>% -->
<!--   rename_with(~new_colnames, c("X0", "X1")) %>% -->
<!--   kable( -->
<!--     booktabs = TRUE, -->
<!--     linesep = "", -->
<!--     caption = caption) %>% -->
<!--   kable_styling(latex_options = c("hold_position"), -->
<!--                 font_size = 9) %>% -->
<!--   footnote(c("Post-Day 29 Cases: COVID-19 primary endpoints that occur at least 7 days after the Day 29 visit."), -->
<!--              threeparttable = TRUE) -->

<!-- ``` -->
