---
knit: "bookdown::render_book"
title: "COVID-19 Baseline Risk Score Analysis Report"
subtitle: '`r source(here::here("_common.R")); paste(study_name, "Study")`'
author: "USG COVID-19 Response Biostatistics Team"
date: "`r format(Sys.time(), '%B %d, %Y')`"
documentclass: book
site: bookdown::bookdown_site
bibliography: [book.bib, packages.bib]
biblio-style: apalike
suppress-bibliography: true
link-citations: yes
colorlinks: yes
graphics: yes
lot: yes
lof: yes
always_allow_html: yes
header-includes:
   - \usepackage{eso-pic,graphicx,transparent,titling,float} # keep titling last!
---


```{r, include = knitr::is_latex_output() & startsWith(study_name, "Mock")}
knitr::asis_output("\\AddToShipoutPictureFG{
  \\AtPageCenter{
    \\makebox[0pt]{\\rotatebox[origin=c]{45}{
      \\scalebox{10}{\\texttransparent{0.3}{MOCK}}}}}}")
```


`r if ( !( grepl("moderna", attr(config::get(config = Sys.getenv("TRIAL")), "config") ) ) )'<!--'`

# Disclaimers

* The data presented in the analysis originated from the Moderna Sponsored mRNA-1273-P301 clinical study and are provided to NIAID in accordance with Clinical Trial Agreement between the parties. The study was funded in part by BARDA under Government Contract No. 75A50120C00034
 
* The preliminary immunogenicity data presented here do not reflect the Sponsors statistical analysis plan and therefore should not be interpreted as a protocol defined read-out of the clinical study.
 
* These data are not to be disclosed without written permission of Moderna.

`r if ( !( grepl("moderna", attr(config::get(config = Sys.getenv("TRIAL")), "config") ) ) ) '-->'`

`r if (knitr::is_latex_output()) '<!--'`

# CoVPN Correlates Analysis Report {-}

## Statistical Analysis Plan {-}

The SAP is available at https://doi.org/10.6084/m9.figshare.13198595

## Reproducibility Notice {-}

This project integrates the virtual environments framework provided by [the
`renv` package](https://rstudio.github.io/renv/) for computational
reproducibility. By taking this approach, all results are generated using a
consistent versioning of both R and several R packages. This version of the
report was built with `r R.version.string`, [pandoc](https://pandoc.org/)
version `r rmarkdown::pandoc_version()`, and the following R packages:

```{r pkg-list, echo=FALSE, results="asis"}
# borrowed from https://github.com/tidymodels/TMwR/blob/master/index.Rmd
deps <- desc::desc_get_deps()
pkgs <- sort(deps$package[deps$type == "Imports"])
pkgs <- sessioninfo::package_info(pkgs, dependencies = FALSE)
df <- tibble::tibble(
  package = pkgs$package,
  version = pkgs$ondiskversion,
  source = gsub("@", "\\\\@", pkgs$source)
)
knitr::kable(df, format = "markdown")
```

To get started with using this project and its `renv` package library, we
first recommend briefly reviewing the [`renv` collaboration
guide](https://rstudio.github.io/renv/articles/collaborating.html).

`r if (knitr::is_latex_output()) '-->'`

<!--chapter:end:index_riskscore.Rmd-->

---
header-includes:
   - \usepackage{float}
output:
  pdf_document: default
  html_document: default
  citation_package: natbib
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r, include = FALSE}
library(here)
here::i_am("riskscore_baseline/report.Rmd")
```

```{r, child=here("riskscore_baseline", 'report_sub.Rmd')}
```

<!--chapter:end:riskscore_baseline/report.Rmd-->

```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running references ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
```



`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:references.Rmd-->

# Appendix

```{r, echo = FALSE, message = FALSE, warning = FALSE}
quiet <- capture.output({
  renv::activate(project = here::here())
  #source(here::here("_common.R"))
})
library(here)
library(digest)

# hash algorithm picked based on https://csrc.nist.gov/projects/hash-functions
hash_algorithm <- "sha256"


#processed_file_digest is created in _common.R, but because the working directory issue, it is not created properly when _common.R is sourced here.
path_to_data = here::here("data_clean", data_name)
if (file.exists(path_to_data)) {
    dat.mock <- read.csv(path_to_data)
    print(paste0("reading data from ",data_name))

    # get hash of commit at HEAD
    commit_hash <- system("git rev-parse HEAD", intern = TRUE)    
    # get hash of input processed data file based on chosen hashing algorithm
    processed_file_digest <- digest(file = path_to_data, algo = hash_algorithm)
    
} else {
    warning("dataset with risk score not available")
  processed_file_digest = ""
}


```

* This report was built from the
  [`CoVPN/correlates_reporting`](https://github.com/CoVPN/correlates_reporting)
  repository with commit hash `r system("git rev-parse HEAD", intern = TRUE)`. A diff of the changes introduced
  by that commit may be viewed at
  https://github.com/CoVPN/correlates_reporting/commit/`r system("git rev-parse HEAD", intern = TRUE)`


* The `r hash_algorithm` hash sum of the processed file, `r paste0("\"",data_name,"\"")`: `r processed_file_digest`

<!--chapter:end:appendix.Rmd-->
