---
output:
  pdf_document: default
  html_document: default
  
---
# Graphical Description of Immunogenicity Data {#immuno-graphical}

```{r immuno-graphical-setup, echo = FALSE, message = FALSE, include=FALSE}
library(here)
library(latex2exp)
library(knitr)

here::i_am("immuno_graphical/report.Rmd")

all_assays <- c("bindSpike", "bindRBD", "bindN", "pseudoneutid50", "pseudoneutid80", "liveneutmn50")

if(include_bindN){
  assay_immuno <- all_assays[all_assays %in% c(assays, "bindN")]
  labels.assays.all <- c("Binding Antibody to N", labels.assays)
  names(labels.assays.all)[1] <- "bindN"
  labels.assays <- labels.assays.all[assay_immuno]
} else {
  assay_immuno <- assays
}
```

```{r immuno-graphical-caption-setup, echo = FALSE, message = FALSE, include=FALSE}

is.ensemble <- study_name=="ENSEMBLE" | study_name=="MockENSEMBLE" # only ENSEMBLE has by country and by HIV group figures

config <- config::get(config = Sys.getenv("TRIAL"))
if.pair <- ifelse(length(config$assays)>1, 1, 0)
if.pos.exist <- ifelse(study_name=="AZD1222", 0, 1)

minority.disclaimer <- switch(study_name, 
                              "COVE"="",
                              "MockCOVE"="",
                              "ENSEMBLE"="These plots are restricted to only United States trial participants.",
                              "MockENSEMBLE"="These plots are restricted to only United States trial participants.",
                              "PREVENT19"="",
                              "AZD1222"="")

neut.marker.captions <- switch(study_name, 
                               "COVE"="The dashed lines in each figure are ULOQ, LLOQ, and positivity cutoffs for binding antibody assays, or ULOQ, LLOQ, and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "MockCOVE"="The dashed lines in each figure are ULOQ, LLOQ, and positivity cutoffs for binding antibody assays, or ULOQ, LLOQ, and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "ENSEMBLE"="The dashed lines in each figure are ULOQ and positivity cut-off from top to bottom for binding antibody assays, or ULOQ and LLOQ for neutralizing antibody assays, from top to bottom respectively.",
                               "MockENSEMBLE"="The dashed lines in each figure are ULOQ and positivity cut-off for binding antibody assays, or ULOQ and LLOQ for neutralizing antibody assays, from top to bottom respectively.",
                               "PREVENT19"="The dashed lines in each figure are ULOQ, positivity cut-off and LLOQ for binding antibody assays, or ULOQ and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               
                               "AZD1222"="The dashed lines in each figure are ULOQ, positivity cut-off and LLOQ for binding antibody assays, or ULOQ and LLOD for neutralizing antibody assays, from top to bottom respectively.")

```

## Pairs plots of antibody markers for overall per-protocal cohort

### Baseline SARS-CoV-2 Negative

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="vaccine"
  
# only doable when there are >1 assays
if (if.pair==1){
    
    for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
      
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_time.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
    
    for (asy in assay_immuno){
      
      asyLabel <- gsub("%","\\\\%", labels.assays[asy])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_assay.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
    
}
```

### Baseline SARS-CoV-2 Positive

```{r, echo=FALSE, results='asis'}

bsero="BaselinePos"
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="vaccine"
  
# only doable when there are >1 assays
if (if.pair==1 & if.pos.exist==1){
    
    for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
      
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_time.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
    
    for (asy in assay_immuno){
      
      asyLabel <- gsub("%","\\\\%", labels.assays[asy])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_assay.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
    
}
```

### Baseline SARS-CoV-2 Positive Placebo Arm

```{r, echo=FALSE, results='asis'}

bsero="BaselinePos"
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="placebo"
  
# only doable when there are >1 assays
if (if.pair==1 & if.pos.exist==1){
    
    for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
      
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_time.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
    
    for (asy in assay_immuno){
      
      asyLabel <- gsub("%","\\\\%", labels.assays[asy])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_assay.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
    
}
```

## RCDF plots of antibody markers for overall per-protocol cohort
```{r, echo=FALSE, results='asis'}
  
for (trt in c("trt_both", "trt_vaccine")){
  trtLabel <- ifelse(trt=="trt_both", "x randomization arm", "vaccine arm")
  
  for (bsero in c("bstatus_both", "bstatus_Neg", "bstatus_Pos")){
    if (bsero=="bstatus_Pos" & if.pos.exist==0) next
    if (trt=="trt_both" & bsero!="bstatus_both") next # trt_both is only for bstatus both
    
    bseroLabel <- ifelse(bsero=="bstatus_both", "by baseline status", ifelse(bsero=="bstatus_Neg", "baseline negative", "baseline positive"))
    
    for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
            
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      for (asy in c("","bAb","nAb")){
        if ( (sum(grepl("bind", assays))==0 & asy=="bAb") | (sum(grepl("pseudo", assays))==0 & asy=="nAb")) next
        if (asy=="" & (trt!="trt_both" | bsero!="bstatus_both")) next  # trt_both & bstatus_both are only for all assays
        if (asy!="" & trt=="trt_both" & bsero=="bstatus_both") next  # trt_both & bstatus_both are only for all assays
        
        res = knitr::knit_child(c(here::here('immuno_graphical', 'report_rcdf.Rmd')), quiet = TRUE)
        cat(res, sep = '\n')
        cat("\\clearpage", sep = '\n')
      }
    }
  }
}
```

\clearpage
## Scatter plots of antibody markers versus age for overall per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Vaccine"
trtLabel="vaccine"
  
for(tp in times[!grepl("Delta", times)]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

### Baseline SARS-CoV-2 Positive

```{r, echo=FALSE, results='asis'}
 
bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Vaccine"
trtLabel="vaccine"

if (if.pos.exist==1) {  
  for(tp in times[!grepl("Delta", times)]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

### Baseline SARS-CoV-2 Positive Placebo Arm

```{r, echo=FALSE, results='asis'}

bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Placebo"
trtLabel="placebo"

if (if.pos.exist==1) {  
  for(tp in times[!grepl("Delta", times)]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

### Baseline SARS-CoV-2 Negative Placebo Arm

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Placebo"
trtLabel="placebo"

for(tp in times[!grepl("Delta", times)]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

\clearpage
## Box plots of antibody markers for overall per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")
  
for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

### Baseline SARS-CoV-2 Positive

```{r, echo=FALSE, results='asis'}

bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

if (if.pos.exist==1){  
  for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

### Baseline negative vs. positive vaccine recipients

```{r, echo=FALSE, results='asis'}

trt="vaccine"
  
for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_neg_vs_pos.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

### Baseline negative vs. positive placebo recipients - New

```{r, echo=FALSE, results='asis'}

trt="placebo"
  
for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_neg_vs_pos.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

\clearpage
## Spaghetti plots of antibody markers over time for the overall per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, fig.cap = paste0("Spaghetti plots of Ab markers over time: baseline negative vaccine + placebo arm"), eval = any(c("B", paste0("Day",timepoints[1]), "Day57") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("spaghetti_plot_BaselineNeg_", study_name, ".png")
))
```

\clearpage
### Baseline SARS-CoV-2 Positive

```{r, fig.cap = paste0("Spaghetti plots of Ab markers over time: baseline positive vaccine + placebo arm"), eval = any(c("B", paste0("Day",timepoints[1]), "Day57") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs",
  paste0("spaghetti_plot_BaselinePos_", study_name, ".png")
))
```

\clearpage
## RCDF plots of antibody markers by demographics for per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by age groups."), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by age groups."), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by age groups."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age groups."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by high-risk condition."), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by high-risk condition."), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by high-risk condition."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by age and high-risk condition."), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by age and high-risk condition."), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by age and high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and high-risk condition."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by sex assigned at birth."), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by sex assigned at birth."), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by sex assigned at birth."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by age and sex assigned at birth."), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by age and sex assigned at birth."), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by age and sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and sex at birth."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by ethnicity."), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by ethnicity."), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by ethnicity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by ethnicity."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by race."), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by race."), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by race."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by race."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_age_minority_group_",
    study_name, ".png"
  )
))
```

```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by country of residence."), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by country of residence."), eval = ("Day57" %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by country of residence."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by country of residence."), eval = ("Delta57overB" %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline negative vaccine arm by HIV positivity."), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselineNeg_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline negative vaccine arm by HIV positivity."), eval = ("Day57" %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselineNeg_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by HIV positivity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselineNeg_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by HIV positivity."), eval = ("Delta57overB" %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselineNeg_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
### Baseline SARS-CoV-2 Positive

```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by age groups."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by age groups."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by age groups."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age groups."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by high-risk condition."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by high-risk condition."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by high-risk condition."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by age and high-risk condition."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by age and high-risk condition."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by age and high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and high-risk condition."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by sex assigned at birth."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by sex assigned at birth."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by sex assigned at birth."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by age and sex assigned at birth."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by age and sex assigned at birth."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by age and sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and sex assigned at birth."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by ethnicity."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by ethnicity."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by ethnicity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by ethnicity."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by race."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by race."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by race."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by race."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by country of residence."), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by country of residence."), eval = ("Day57" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by country of residence."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by country of residence."), eval = ("Delta57overB" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive vaccine arm by HIV positivity."), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_vaccine_BaselinePos_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive vaccine arm by HIV positivity."), eval = ("Day57" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_vaccine_BaselinePos_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by HIV positivity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_vaccine_BaselinePos_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by HIV positivity."), eval = ("Delta57overB" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_vaccine_BaselinePos_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
### Baseline SARS-CoV-2 Positive Placebo Arm

```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by age groups."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by age groups."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by age groups."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by age groups."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by high-risk condition."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by high-risk condition."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by high-risk condition."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by age and high-risk condition."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by age and high-risk condition."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by age and high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by age and high-risk condition."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_age_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by sex assigned at birth."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by sex assigned at birth."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by sex assigned at birth."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by age and sex assigned at birth."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by age and sex assigned at birth."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by age and sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by age and sex assigned at birth."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_age_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by ethnicity."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by ethnicity."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by ethnicity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by ethnicity."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by race."), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by race."), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by race."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by race."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by age and dichotomous classification of race and ethnic group.",minority.disclaimer), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_age_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by country of residence."), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by country of residence."), eval = ("Day57" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by country of residence."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by country of residence."), eval = ("Delta57overB" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," Ab markers: baseline positive placebo arm by HIV positivity."), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day",timepoints[1],"_trt_placebo_BaselinePos_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 Ab markers: baseline positive placebo arm by HIV positivity."), eval = ("Day57" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Day57_trt_placebo_BaselinePos_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by HIV positivity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta",timepoints[1],"overB_trt_placebo_BaselinePos_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("RCDF plots for D57 fold-rise over D1 Ab markers: baseline positive placebo arm by HIV positivity."), eval = ("Delta57overB" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "Marker_Rcdf_Delta57overB_trt_placebo_BaselinePos_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
## Boxplots of antibody markers by demographics for per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by age group.", neut.marker.captions), eval = (paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by age group.", neut.marker.captions), eval = ("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by age group."), eval=(paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age group."), eval=("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by high-risk condition.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by high-risk condition.", neut.marker.captions), eval=("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by high-risk condition."), eval=(paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by high-risk condition."), eval=("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by age and high-risk condition.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by age and high-risk condition.", neut.marker.captions), eval=("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by age and high-risk condition."), eval=(paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and high-risk condition."), eval=("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by sex assigned at birth.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by sex assigned at birth.", neut.marker.captions), eval=("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by sex assigned at birth."), eval=(paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by sex assigned at birth."), eval=("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by age and sex assigned at birth.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by age and sex assigned at birth.", neut.marker.captions), eval=("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by age and sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and sex assigned at birth."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by ethnicity.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by ethnicity.", neut.marker.captions), eval=("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by ethnicity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by ethnicity."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by race.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by race.", neut.marker.captions), eval=("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by race."), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by race."), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=(paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=(paste0("Day",timepoints[1]) %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=("Day57" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by country of residence.", neut.marker.captions), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by country of residence.", neut.marker.captions), eval = ("Day57" %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by country of residence."), eval=(paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by country of residence."), eval=("Delta57overB" %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline negative vaccine arm by HIV positivity.", neut.marker.captions), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselineNeg_trt_Vaccine_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline negative vaccine arm by HIV positivity.", neut.marker.captions), eval = ("Day57" %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselineNeg_trt_Vaccine_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline negative vaccine arm by HIV positivity."), eval=(paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselineNeg_trt_Vaccine_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline negative vaccine arm by HIV positivity."), eval=("Delta57overB" %in% times) & is.ensemble}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselineNeg_trt_Vaccine_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
### Baseline SARS-CoV-2 Positive

```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by age group.", neut.marker.captions), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by age group.", neut.marker.captions), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by age group."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age group."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by high-risk condition.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by high-risk condition.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by high-risk condition."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by age and high-risk condition.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by age and high-risk condition.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by age and high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and high-risk condition."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by sex assigned at birth.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by sex assigned at birth.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by sex assigned at birth."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by age and sex assigned at birth.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by age and sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and sex assigned at birth."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by ethnicity", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by ethnicity.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by ethnicity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by ethnicity."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by race.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by race.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by race."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by race."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by country of residence.", neut.marker.captions), eval=FALSE, eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by country of residence.", neut.marker.captions), eval=FALSE, eval = ("Day57" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by country of residence."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by country of residence."), eval = ("Delta57overB" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive vaccine arm by HIV positivity.", neut.marker.captions), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Vaccine_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive vaccine arm by HIV positivity.", neut.marker.captions), eval = ("Day57" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Vaccine_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive vaccine arm by HIV positivity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Vaccine_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive vaccine arm by HIV positivity."), eval = ("Delta57overB" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Vaccine_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
### Baseline SARS-CoV-2 Positive Placebo Arm
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by age group.", neut.marker.captions), eval = (paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by age group.", neut.marker.captions), eval = ("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by age group."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by age group."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_age_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by high-risk condition.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by high-risk condition.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by high-risk condition."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by age and high-risk condition.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by age and high-risk condition.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by age and high-risk condition."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by age and high-risk condition."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_age_x_risk_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by sex assigned at birth.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by sex assigned at birth.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by sex assigned at birth."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_sex_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by age and sex assigned at birth.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by age and sex assigned at birth.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by age and sex assigned at birth."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by age and sex assigned at birth."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_age_x_sex_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by ethnicity", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by ethnicity.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by ethnicity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by ethnicity."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_ethnicity_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by race.", neut.marker.captions), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by race.", neut.marker.captions), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by race."), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by race."), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_race_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_minority_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by age and dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=(paste0("Day",timepoints[1]) %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by age and dichotomous classification of race and ethnic group.", neut.marker.captions, minority.disclaimer), eval=("Day57" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = (paste0("Delta",timepoints[1],"overB") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by age and dichotomous classification of race and ethnic group.", minority.disclaimer), eval = ("Delta57overB" %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_age_x_minority_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by country of residence.", neut.marker.captions), eval=FALSE, eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by country of residence.", neut.marker.captions), eval=FALSE, eval = ("Day57" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by country of residence."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by country of residence."), eval = ("Delta57overB" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_country_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," Ab markers: baseline positive placebo arm by HIV positivity.", neut.marker.captions), eval = (paste0("Day",timepoints[1]) %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day",timepoints[1],"_BaselinePos_trt_Placebo_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 Ab markers: baseline positive placebo arm by HIV positivity.", neut.marker.captions), eval = ("Day57" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Day57_BaselinePos_trt_Placebo_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D",timepoints[1]," fold-rise over D1 Ab markers: baseline positive placebo arm by HIV positivity."), eval = (paste0("Delta",timepoints[1],"overB") %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta",timepoints[1],"overB_BaselinePos_trt_Placebo_by_hiv_group_",
    study_name, ".png"
  )
))
```

\clearpage
```{r, fig.cap = paste0("Boxplots of D57 fold-rise over D1 Ab markers: baseline positive placebo arm by HIV positivity."), eval = ("Delta57overB" %in% times) & is.ensemble & if.pos.exist==1}
include_graphics(here(
  "immuno_graphical", "figs", "demographics",
  paste0(
    "boxplots_Delta57overB_BaselinePos_trt_Placebo_by_hiv_group_",
    study_name, ".png"
  )
))
```